\documentclass[11pt, a4paper]{article}
\usepackage[inner=1in,outer=1in,top=1in,bottom=1in]{geometry}
\pagestyle{empty}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw}
\usepackage[usenames,dvipsnames]{color}
\definecolor{darkblue}{rgb}{0,0,.6}
\definecolor{darkred}{rgb}{.7,0,0}
\definecolor{darkgreen}{rgb}{0,.6,0}
\definecolor{red}{rgb}{.98,0,0}
\usepackage[colorlinks,pdfusetitle,urlcolor=darkblue,citecolor=darkblue,linkcolor=darkred,bookmarksnumbered,plainpages=false]{hyperref}
%\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{\CourseTitle} }
%\chead{ \fancyplain{}{} }
\rhead{ \fancyplain{}{\CourseSemester \CourseYear} }
%\rfoot{\fancyplain{}{page \thepage\ of \pageref{LastPage}}}
\fancyfoot[RO, LE] {page \thepage\ of \pageref{LastPage} }
\thispagestyle{plain}
\usepackage{tabularx}
\usepackage{amsmath}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{xspace}
\newcommand{\CourseNumber}{NPRE555}
\newcommand{\CourseTitle}{Reactor Theory I\xspace}%
\newcommand{\CourseSemester}{Fall\xspace}%
\newcommand{\CourseYear}{2025\xspace}%
\newcommand{\CourseDays}{MW\xspace}%
\newcommand{\CourseStart}{1:00pm\xspace}%
\newcommand{\CourseEnd}{2:50pm\xspace}%
\newcommand{\CourseInstructor}{Prof. Kathryn Huff}
\newcommand{\CourseInstructorEmail}{kdhuff@illinois.edu}
\newcommand{\CourseRoom}{\href{https://maps.app.goo.gl/mv1KTevxS3pmbSim6}{106B3 Engineering Hall}\xspace}%
\newcommand{\CourseBuilding}{\xspace}%
\newcommand{\CourseUniversity}{University of Illinois, Urbana-Champaign\xspace}%
\newcommand{\HuffOffice}{111B Talbot Laboratory\xspace}
\newcommand{\TeachingAssistant}{TA Name\xspace}%
\newcommand{\TAOfficeHourDays}{Wednesdays\xspace}%
\newcommand{\TAOfficeHourStart}{1:00pm\xspace}%
\newcommand{\TAOfficeHourEnd}{3:00pm\xspace}%
\newcommand{\TAOfficeHourPlace}{123 Talbot Laboratory\xspace}
%\newcommand{\Course<++>}{<++>}
%\newcommand{\Course<++>}{<++>}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\CourseNumber: \CourseTitle\\}
\author{\CourseUniversity}
\date{\CourseSemester \CourseYear}
\begin{document}
\maketitle
%\setlength{\unitlength}{1in}
\renewcommand{\arraystretch}{2}
\begin{center}
\begin{table}[h]
\begin{tabularx}{\textwidth}{rXrX}
\hline
\textbf{Instructor:} & \CourseInstructor & \textbf{Time:} & \CourseDays \CourseStart -- \CourseEnd \\
\textbf{Email:} &  \href{mailto:\CourseInstructorEmail}{\CourseInstructorEmail} & \textbf{Place:} & \CourseRoom \CourseBuilding\\
\hline
\end{tabularx}

\end{table}
\end{center}

\paragraph{Course Pages:}
\begin{enumerate}
        \item \url{https://canvas.illinois.edu/courses/57908}
        \item \url{https://github.com/katyhuff/\CourseNumber}
        \item 
                \url{https://mediaspace.illinois.edu/playlist/dedicated/1_fetbf4t5/}
\end{enumerate}

%\paragraph{TA Office Hours:} The teaching assistant for the course,
%\TeachingAssistant, will hold office hours \TAOfficeHourDays from
%\TAOfficeHourStart to \TAOfficeHourEnd in \TAOfficeHourPlace.

\paragraph{Office Hours:} Prof. Huff will hold office hours by appointment 
only and prefers to meet in her office, \HuffOffice. Please make an appointment at 
\url{https://katyhuff.youcanbook.me}. If your colleagues might be helpful, please 
discuss your questions with them directly before scheduling office hours.

\paragraph{Main References:}
A few essential references for this course will be assigned as readings and 
will be the source of homework problems. The required texts for this course are 
\cite{stacey_nuclear_2007} and \cite{bell_nuclear_1970}. I also recommend 
\cite{duderstadt_transport_1979} for conceptual review and 
\cite{lewis_computational_1993} for computational methods details.
Electronic copies of these books can be found online if they are not available
in the UIUC library.

\bibliographystyle{unsrt}
\renewcommand{\refname}{\normalfont\selectfont\normalsize}\vspace{-1cm}
\bibliography{bibliography}

\paragraph{Objectives:}
\begin{itemize}
\item Advanced development of neutron transport theory
\item  neutron slowing-down,
\item resonance absorption,
\item  approximations to the transport equation,
\item  direct numerical methods and other techniques of approximation theory 
        applied to the neutron transport equation,
\item  and advanced topics. 
\end{itemize}

\paragraph{Prerequisites:}
\begin{itemize}
\item NPRE455 (waived for Physics Majors) 
\end{itemize}

\paragraph{Grading Policy:} Grades will be assigned as a weighted sum of the
following work.

\begin{table}[h]
\begin{tabularx}{\textwidth}{Xr}
        \textbf{Work} & \textbf{Weight} \\
\hline
\textbf{Homework}    & (50\%)  \\
\textbf{Project 1}    & (15\%)  \\
\textbf{Project 2}    & (15\%)  \\
\textbf{Final Project}  & (20\%)  \\
\hline
\textbf{Total}       & (100\%)\\
\end{tabularx}
\end{table}

\paragraph{Important Dates:}
\begin{center} \begin{minipage}{3.8in}
\begin{flushleft}
Project \#1      \dotfill 1:00pm, Monday October 6, 2025 \\
Project \#2      \dotfill 1:00pm, Monday November 10, 2025\\
%Project Deadline \dotfill ~Month Day \\
Final Project    \dotfill 5:00pm, Wednesday Dec. 17, 2025\\
Presentation \dotfill 7:00pm--10:00pm, Wednesday Dec. 17, 2025\\
\end{flushleft}
\end{minipage}
\end{center}

\paragraph{Class Policies:}

\begin{itemize}
\item[] \textbf{Integrity:} This is an institution of higher learning.
        Do not undermine its integrity. Academic dishonesty may result in a failing grade. 
                Every student is expected to review and abide by the Academic 
                Integrity Policy. Ignorance is not an excuse for any academic 
                dishonesty. It is your responsibility to read this policy to 
                avoid any misunderstanding.  Note the 
                \href{https://provost.illinois.edu/policies/policies/academic-integrity/students-quick-reference-guide-to-academic-integrity/}{Student's 
                Quick Reference Guide to Academic Integrity} and the 
                \href{https://studentcode.illinois.edu/article1/part4/1-401/}{Academic 
                Integrity Policy and Procedure}.
\item[] \textbf{Attendance:} 
        Regular class attendance is expected of all students at the university. 
                Request approval for absence for extenuating circumstances 
                prior to absence.  If you are or become ill, please communicate 
                with me and the Dean of Students regarding your expected need 
                for accommodation in this class. I am willing, able, and ready 
                to make neccessary accommodations.
\item[] \textbf{Electronics:} 
        Active participation is essential and expected.
        Accordingly, students should only use electronic devices (laptop,
        tablets, etc.) during class if engaging in computational 
        exercises or taking notes.
\item[] \textbf{Collaboration:} Collaboratively reviewing course materials and 
        working through homework problems with fellow students can be 
                enriching.  This is recommended.  However, unless otherwise 
                instructed, homework assignments are to be completed with 
                individual attainment in mind and materials submitted as 
                homework or computational assignments should be the result of 
                one's own independent work.
\item[] \textbf{Late Work:} Late work has a halflife of 1 hour. That is, 
        adjusted for lateness, your grade $G(t)$ is a decaying percentage of 
                the raw grade $G_0$. An assignment turned in $t$ hours late 
                will receive a grade according to the following relation:
\begin{align*}
        G(t) &= G_0e^{-\lambda t}
        \intertext{where}
        G(t) &= \mbox{grade adjusted for lateness}\\
        G_0 &= \mbox{raw grade}\\
        \lambda &= \frac{ln(2)}{t_{\frac{1}{2}}} = \mbox{decay constant} \\
        t &= \mbox{time elapsed since due [hours]}\\
        t_{1/2} &= 1 = \mbox{half-life [hours]} \\
\end{align*}
\item[] \textbf{Make-up Work:} There will be no negotiation about late work 
        except in the case of absence documented by an 
                \href{https://odos.illinois.edu/community-of-care/resources/students/absence-letters/}{Absence Letter}
                from the Dean of Students.  
                Please note that such a letter is appropriate 
                for many types of conflicts, but that religious conflicts 
                require special early handling. In accordance with university 
                policy, students seeking an excused absence for religious 
                reasons should complete the Request for Accommodation for 
                Religious Observances Form, which can be found on the Office of 
                the Dean of Students website. The deadline for submitting this 
                form is fairly early in the semester.
\item[]\textbf{Emergency response recommendations} can be found at
        \href{http://police.illinois.edu/em/planning/emergency-response-guide/}{this website}.
        I encourage you to review this website and the campus building
        \href{http://police.illinois.edu/emergency-preparedness/building-emergency-action-plans/}{floor
        plans website} within the first 10 days of class.  If you want to
        better prepare yourself for any of these situations, visit
        \href{http://police.illinois.edu/safe}{police.illinois.edu/safe}. Remember you can sign up for emergency
        text messages at \href{http://emergency.illinois.edu}{emergency.illinois.edu}.

\item[]\textbf{Grade Disputes:} It is important that you understand and agree
        with the grade you receive on assignments. If you would like
        to dispute your score, you must send an explanation by email to Prof.
        Huff within one week of recieving the grade.
        \textbf{Do not expect me to regrade anything while in conversation with
        you} as that would not be fair to the other students in the class, whose
        homeworks were graded without them present.  If you request a regrade,
        be aware that the entire assignment will be regraded and is subject to
        double-jeopardy: it is possible that your score will go down.
        Regrade requests should be based on an error on my part (e.g., adding
        up the points incorrectly) or what you suspect is a misunderstanding of
        your work (e.g., arriving at the correct answer using an unexpected
        technique). Regrade requests that argue with the rubric (e.g., ``this is
        wrong, but you took too many points off'') will be returned without
        consideration.
        \textbf{Your work should stand alone.} If an assignment is disorganized or
        ambiguous, and requires an extensive explanation to the grader, you
        will likely still lose points. The homeworks not only evaluate your
        understanding of the material - they also evaluate your ability to
        communicate that understanding clearly and concisely.
\item[]\textbf{Anti-Racism and Inclusivity Statement} The Grainger College of
        Engineering is committed to the creation of an anti-racist, inclusive
        community that welcomes diversity along a number of dimensions,
        including, but not limited to, race, ethnicity and national origins,
        gender and gender identity, sexuality, disability status, class, age,
        or religious beliefs. The College recognizes that we are learning
        together in the midst of the Black Lives Matter movement, that Black,
        Hispanic, and Indigenous voices and contributions have largely either
        been excluded from, or not recognized in, science and engineering, and
        that both overt racism and micro-aggressions threaten the well-being of
        our students and our university community.
        The effectiveness of this course is dependent upon each of us to create
        a safe and encouraging learning environment that allows for the open
        exchange of ideas while also ensuring equitable opportunities and
        respect for all of us. Everyone is expected to help establish and
        maintain an environment where students, staff, and faculty can
        contribute without fear of personal ridicule, or intolerant or
        offensive language. If you witness or experience racism,
        discrimination, micro-aggressions, or other offensive behavior, you are
        encouraged to bring this to the attention of the course director if you
        feel comfortable. You can also report these behaviors to the
        \href{https://diversity.illinois.edu/diversity-campus-culture/belonging-resources/}{Campus
        Belonging portal.}
         Based on your report, Campus Belonging will follow up and reach
        out to students to make sure they have the support they need to be
        healthy and safe. If the reported behavior also violates university
        policy, staff in the Office for Student Conflict Resolution may respond
        as well and will take appropriate action.
\item[]\textbf{Disability-Related Accommodations:} The University of Illinois Champaign-Urbana, is committed to ensuring that all students, including students with disabilities, do not experience barriers to learning and participating fully in class. Students who have a letter of accommodation from DRES are advised to share that with instructors as soon as possible to ensure accommodation needs can be discussed and met.

To obtain disability-related academic accommodations, disabled students must contact Disability Resources and Educational Services (DRES) as soon as possible. To contact DRES, please visit 1207 S. Oak Street, Champaign, call 217.333.1970, email disability@illinois.edu, or visit the DRES website: \href{https://www.disability.illinois.edu}{disability.illinois.edu}. 

\item[]\textbf{Family Educational Rights and Privacy Act (FERPA):}
Any student who has suppressed their directory information pursuant to Family
Educational Rights and Privacy Act (FERPA) should self-identify to the
instructor to ensure protection of the privacy of their attendance in this
course. See \href{https://registrar.illinois.edu/ferpa/}{this
link} for more information on FERPA.

\item[]\textbf{Religious Observances}
It is the policy of the University of Illinois Urbana-Champaign to reasonably accommodate its students’ religious beliefs, observances, and practices that conflict with a student’s class attendance or participation in a scheduled examination or work requirement, consistent with state and federal law.  Students must make requests for accommodation in advance of the conflict to allow time for both consideration of the request and alternate procedures to be prepared.  Requests should be directed to the instructor.  The Office of the Dean of Students provides an optional resource on its website to assist students in making such requests.     
\href{https://odos.illinois.edu/resources/students/religious-observances}{this
link} to request appropriate accommodations. This should be done in the first two weeks of classes.
\end{itemize}

\paragraph{Land Acknowledgement: }As a land-grant institution, the University of Illinois Urbana-Champaign has a responsibility to acknowledge the historical context in which it exists. In order to remind ourselves and our community, we begin this course with the following statement. We are currently on the lands of the Peoria, Kaskaskia, Piankashaw, Wea, Miami, Mascoutin, Odawa, Sauk, Mesquaki, Kickapoo, Potawatomi, Ojibwe, and Chickasaw Nations. It is necessary for us to acknowledge these Native Nations and for us to work with them as we move forward as an institution. Over the next 150 years, we will be a vibrant community inclusive of all our differences, with Native peoples at the core of our efforts. \href{https://chancellor.illinois.edu/land_acknowledgement.html}{Office of the Chancellor Land Acknowledgement Statement}.

\paragraph{Sexual Misconduct Reporting Obligation:} The University of Illinois is committed to combating sexual misconduct. Faculty and staff members are required to report any instances of sexual misconduct to the University’s Title IX Office. In turn, an individual with the Title IX Office will provide information about rights and options, including accommodations, support services, the campus disciplinary process, and law enforcement options.

A list of the designated University employees who, as counselors, confidential
advisors, and medical professionals, do not have this reporting responsibility
and can maintain confidentiality, can be found
\href{https://wecare.illinois.edu/resources/students/#confidential}{here}.
Other information about resources and reporting is available here: wecare.illinois.edu.

\paragraph{Other Resources:}
University students typically experience a wide range of stressors during their
time on campus. Accordingly, campus resources exist to help students manage
stress levels, mental health, physical health, and emergencies while navigating
this environment. I hope you will take advantage of these campus resources as
soon as they can be of help.

\begin{itemize}
\item \href{https://campusrec.illinois.edu/}{The Campus Recreational Centers}
\item \href{http://counselingcenter.illinois.edu/}{The Counseling Center}
\item \href{http://odos.illinois.edu/emergency/}{The McKinley Mental Health Clinic}
\item \href{https://odos.illinois.edu/community-of-care/emergency-dean}{The Emergency Dean}
\end{itemize}


\pagebreak
\FloatBarrier
\renewcommand{\arraystretch}{1}
\begin{table}[h]
\begin{center}
\begin{tabular}{lllcllll}
\multicolumn{8}{c}{\textbf{Course Schedule:}\textit{ Note that this schedule is subject to change}}\\
&&&&&&&\\
\textbf{Date} & \textbf{Week} & \textbf{Day} & \textbf{Unit} & \textbf{Chap.} & \textbf{Chap.} & \textbf{HW} & \textbf{HW}\\
              &  &  & & \textbf{Stacey}& \textbf{B\&G} & \textbf{Given} & \textbf{Due}\\
\hline
\hline
08-25 & 1 & M  & Transport Eqn.          & 9    & 1    & HW1 &     \\
08-27 & 1 & W  & Transport Eqn.          & 9    & 1    & CP1 &     \\
09-01 & 2 & M  & Boundary Conds.         & 9    & 1    & HW2 & HW1 \\
09-03 & 2 & W  & Boundary Conds.         & 9    & 1    &     &     \\
09-08 & 3 & M  & Angle \& Energy         & 9    & 1    & HW3 & HW2 \\
09-10 & 3 & W  & Angle \& Energy         & 9    & 1    &     &     \\
09-15 & 4 & M  & Monte Carlo             & 9.12 & 1\&2 & HW4 & HW3 \\
09-17 & 4 & W  & Monte Carlo             & 9.12 & 1\&2 &     &     \\
09-22 & 5 & M  & Monte Carlo             & 9.12 & 1\&2 & HW5 & HW4 \\
09-24 & 5 & W  & Monte Carlo             & 9.12 & 1\&2 &     &     \\
09-29 & 6 & M  & $P_N$                   & 9    & 3    & HW6 & HW5 \\
10-01 & 6 & W  & $P_N$                   & 9    & 3    &     &     \\
10-06 & 7 & M  & Multi-group $P_N$       & 9    & 4    & CP2 & CP1 \\
10-08 & 7 & W  & Multi-group $P_N$       & 9    & 4    &     &     \\
10-13 & 8 & M  & $P_N$ Eigenvalue Calcs. & 9    & 4    & HW7 & HW6 \\
10-15 & 8 & W  & $P_N$ Eigenvalue Calcs. & 9    & 4    &     &     \\
10-20 & 9 & M  & $S_N$                   & 9    & 5    & HW8 & HW7 \\
10-22 & 9 & W  & $S_N$                   & 9    & 5    &     &     \\
10-27 & 10 & M & $S_N$                   & 9    & 5    & HW9 & HW8 \\
10-29 & 10 & W & $S_N$                   & 9    & 5    &     &     \\
11-03 & 11 & M & Adjoint Eqn.            & 13   & 6    & HW10& HW9 \\
11-05 & 11 & W & Adjoint Eqn.            & 13   & 6    &     &     \\
11-10 & 12 & M & Perturbation Theory     & 13   & 6    & CP3 & CP2 \\
11-12 & 12 & W & Variational Methods     &      &      &     &     \\
11-17 & 13 & M & Neutron Slowing Down    & 10   & 7    & HW11& HW10\\
11-19 & 13 & W & Neutron Slowing Down    & 10   & 7    &     &     \\
11-24 & 14 & M & \textbf{Fall Break}     &      &      &     &     \\
11-26 & 14 & W & \textbf{Fall Break}     &      &      &     &     \\
12-01 & 15 & M & Neutron Thermalization  & 11   & 7    & HW12& HW11\\
12-03 & 15 & W & Neutron Thermalization  & 11   & 7    &     &     \\
12-08 & 16 & M & Resonance Absorption    & 12   & 11   &     & HW12\\
12-10 & 16 & W & Resonance Absorption    & 12   & 11   &     &     \\
12-17 & 17 & W & \textbf{Final Presentation} &  &      & CP3 &     \\
\end{tabular}
\end{center}
\end{table}
%%%%%% THE END 
\end{document} 
