% use the answers clause to get answers to print; otherwise leave it out.
\documentclass[11pt,answers,addpoints]{exam}
%\documentclass[11pt,addpoints]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace}
\usepackage{graphicx}

% By default LaTeX uses large margins.  This doesn't work well on exams; problems
% end up in the "middle" of the page, reducing the amount of space for students
% to work on them.
\usepackage[margin=1in]{geometry}
\usepackage{enumerate}
\usepackage[hidelinks]{hyperref}

% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{NPRE 555}
\newcommand{\term}{Fall 2025}
\newcommand{\assignment}{HW 1}
\newcommand{\duedate}{2025.09.01}
%\newcommand{\timelimit}{50 Minutes}

\newcommand{\nth}{n\ensuremath{^{\text{th}}} }
\newcommand{\ve}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\Macro}{\ensuremath{\Sigma}}
\newcommand{\vOmega}{\ensuremath{\hat{\Omega}}}

% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

%\unframedsolutions

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\assignment\ - Page \thepage\ of \numpages}{Due \duedate}
\runningheadrule

\class \hfill \term \\
\assignment \hfill Due \duedate\\
\rule[1ex]{\textwidth}{.1pt}
%\hrulefill

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
        \item Show your work. 
        \item This work must be submitted online as a \texttt{.pdf} through Canvas.
        \item Work that appears to have been handwritten with a dull pencil or 
                photographed with a potato will not be graded generously. 
                Typset your homework if possible. Write and digitize carefully if not.
        \item Work completed with LaTeX earns 1 extra point. Submit 
                source file (\texttt{.tex}) along with 
                the \texttt{.pdf} file.
        \item If this work is completed with the aid of a numerical program 
                (such as Python, Wolfram Alpha, or MATLAB) all scripts and data 
                must be submitted in addition to the \texttt{.pdf}.
        \item If you work with anyone else, document what you worked on together.
\end{itemize}
\rule[1ex]{\textwidth}{.1pt}

% ---------------------------------------------
\begin{questions}
        % ---------------------------------------------
        \question In this class, Prof. Huff will call on you randomly.
        She would like to address you respectfully and correctly. 
        \begin{parts}
                \part[10] What is your preferred full name?
                \begin{solution}
                        For example, ``Jean-Baptiste Emanuel Zorg''.
                \end{solution}
                \part[10] What are your gender pronouns?
                \begin{solution}
                        they/them, she/her, he/him, he/they, etc.
                \end{solution}
                \part[20] Prof. Huff generally uses the honorific form when 
                addressing students during class (``Mr. 
                Dallas'', ``Ms. Iceborg'', ``Mx. Rhod'', ``Dr. Who'' ). Do you have a 
                preference for how she should refer to you in the honorific 
                form?
                \begin{solution}
                        
                \end{solution}
        \end{parts}

        % ---------------------------------------------
        \question[20] Please create a GitHub account if you do not yet have one. 
        What is your GitHub username?
        \begin{solution}
                Solution here.
        \end{solution}

        % ---------------------------------------------
        \question[20] Will late work be accepted?
        \begin{solution}
                solution here
        \end{solution}


        % ---------------------------------------------
        \question[10] Where is the instructor's office?
        \begin{solution}
                solution here
        \end{solution}

        % ---------------------------------------------
        \question[10] How can you arrange a time to meet with Prof. Huff?
        \begin{solution}
                solution here
        \end{solution}

        % ---------------------------------------------
        \question[10] At what date and time will the final presentations for this course take place?
        \begin{solution}
                solution here
        \end{solution}

\end{questions}



%\bibliographystyle{plain}
%\bibliography{hw01}
\end{document}
